Safe Memory Regions for Big Data Processing

### 2016-06-22 paper/type-inference.tex
type inference

\begin{definition}
\emph{(\textbf{Constraint Satisfaction Problem (CSP)})}
A constraint satisfaction problem is a tuple
$(\bar{\pi}, \bar{\rho}, \bar{\varphi}, \regionDeltaMap, \predDeltaMap, C)$,
where $\bar{\pi}$ is a set of region constants,
$\bar{\rho}$ is a set of region variables,
$\bar{\varphi}$ is a set of predicate variables,
$\regionDeltaMap : \bar{\rho} \rightarrow 2^{\bar{\pi}}$ is a function that
specifies a unification domain for each region variable,
$\predDeltaMap : \bar{\varphi} \rightarrow 2^{\bar{\pi}}$ is a function that
specifies the domain for each predicate variable,
and $C$ is a set of validity constraints, where the $i$'th validity constraint
assumes one of the following forms:
\begin{center}
\(
    \isvalid{\phictxt^{i} \conj \varphi}
            {\phicstr^{i}}\qquad
    \isvalid{\phictxt^{i} \conj \varphi}
            {F_i(\varphi)}
\)
\end{center}
The solution to the constraint satisfaction problem is a pair $(\regionSubstFn,\predSubstFn)$,
where $\regionSubstFn$ is a map from $\rhobar$ to $\bar{\pi}$
and $\predSubstFn$ is a map from $\bar{\varphi}$ to a region-constraint formula such that
\begin{itemize}
  \item $\regionSubstFn(\rho) \in \regionDeltaMap(\rho)$, for every $\rho \in \bar{\rho}$,

  \item $\predSubstFn$ is well-formed under $\predDeltaMap$
    (i.e., $\tywf{\predDeltaMap(\varphi)}{\predSubstFn(\varphi)}$, for every $\varphi \in \bar{\varphi}$).

>>>>

\begin{definition}
\emph{(\textbf{Constraint Satisfaction Problem (CSP)})}
A constraint satisfaction problem is a tuple
$(\regionConstants, \regionVars, \predVars, \regionDeltaMap, \predDeltaMap, \constraintSet)$,
where $\regionConstants$ is a set of region constants,
$\regionVars$ is a set of region variables,
$\predVars$ is a set of predicate variables,
$\regionDeltaMap : \regionVars \rightarrow 2^{\regionConstants}$ is a function that
specifies a unification domain for each region variable,
$\predDeltaMap : \predVars \rightarrow 2^{\regionConstants}$ is a function that
specifies the domain for each predicate variable,
and $\constraintSet$ is a set of validity constraints in one of the following forms:
\begin{center}
\(
    \isvalid{\phictxt \conj \varphi}{\phicstr}\qquad
    \isvalid{\phictxt \conj \varphi}{F(\varphi)}
\)
\end{center}
The solution to the constraint satisfaction problem is a pair $(\regionSubstFn,\predSubstFn)$,
where $\regionSubstFn$ is a map from $\regionVars$ to $\regionConstants$
and $\predSubstFn$ is a map from $\predVars$ to a region-constraint formula such that
\begin{itemize}
  \item $\regionSubstFn(\rho) \in \regionDeltaMap(\rho)$, for every $\rho \in \regionVars$,

  \item $\predSubstFn$ is well-formed under $\predDeltaMap$
    (i.e., $\tywf{\predDeltaMap(\varphi)}{\predSubstFn(\varphi)}$, for every $\varphi \in \predVars$).
